Presentation Title

### 2017-06-22 thesis/chapters/ch3-analysis.tex
Fix up performance analysis

\section{Performance}
TODO intro

\subsection{Message Complexity of ACS}
\label{sec:acs-complexity}
The message complexity of ACS is $O(n^2|v| + \lambda n^3 \log n)$~\cite{miller2016honey},
where $|v|$ is the size of largest message and $\lambda$ is the security parameter.
Note that the security parameter is the same as the one for our random oracle described in \Cref{sec:model-assumptions}.
In particular, it is from the use of $\textsf{H}(\cdot)$ in the reliable broadcast phase in ACS.
In our system, we wish to understand the scalability properties.
Thus we consider the complexity as a function of $N$ rather than $n$ or $\lambda$.
Since $|v|$ is at most all the CP blocks from every node, we have $|v| = N$.
Therefore the message complexity of ACS in our system is $O(N)$.
Since we use a constant $n$, $O(N)$ message complexity also holds for a single facilitator.

@@

\subsection{Bandwidth Requirement for Transactions}
To make and validate a transaction, the bandwidth required is of $O(l)$,
where $l$ is the length of the agreed fragment.
This can be seen from the fact that the largest message by far is the \texttt{vd\_resp} message,
which contains the agreed fragment,
the other messages (\texttt{tx\_req}, \texttt{tx\_resp} and \texttt{vd\_req}) are constant factors.
If we assume that every node performs transactions at a constant rate of $r_{\text{tx}}$ per second.
Then $l = (D_{\text{acs}} + D) \cdot r_{\text{tx}}$, where $D_{\text{acs}}$ is the duration an instance of ACS.
But from \Cref{sec:acs-complexity}, we know that $D_{\text{acs}}$ is of $O(N)$, thus the bandwidth per transaction is $O(N)$.
% TODO how does message complexity translate to time complexity?
% TODO computational task minimal compared to messages, thus the sending of message is expensive?
This is natural because consensus duration would be longer if there are more CP blocks, which means that the agreed fragments are longer.
This behaviour is also verified experimentally in \Cref{ch:implementation}.

\subsection{Global Throughput}
Suppose every node has some fixed bandwidth capacity $C$ (unit of communication per second),
they make transactions at $r_{\text{tx}}$ per second.
Then we have the inequality $C \ge r_{\text{tx}} l$, where $l$ is the length of the the agree fragment as before.
Rearranging, we get $\frac{C}{l} \ge r_{\text{tx}}$.
With this, we consider two cases, first is  when all the nodes are running at maximum capacity.
Recall that $l$ is of $O(N)$, so as the the population increases, 
the transaction rate must decrease in order to maintain the inverse relationship,
thus $r_\text{tx}$ is of $O(N^{-1})$. % TODO is this formal? use omega?
Therefore, the global throughput would be $O(N^{-1})N = O(1)$.
In the second case, nodes are not running at maximum capacity and $r_{\text{tx}}$ is maintained.
Therefore, if every node runs at $r_{\text{tx}}$,
the global throughput becomes $O(N)$ until $N$ is too large and we go back to the first case.

>>>>

\section{Performance}
This section aims to (analytically) answer our research question.
That is, does the global throughput increase linearly with respect to the population size?
We begin by looking at the communication and time complexity of ACS,
and then the bandwidth requirement for a single transaction.
These are prerequisites of the global throughput analysis.

\subsection{Communication Complexity of ACS}
\label{sec:acs-complexity}
The communication complexity of ACS is $O(n^2|v| + \lambda n^3 \log n)$~\cite{miller2016honey},
where $|v|$ is the size of largest message and $\lambda$ is the security parameter.
Note that the security parameter is the same as the one for our random oracle described in \Cref{sec:model-assumptions}.
In particular, it is from the use of $\textsf{H}(\cdot)$ in the reliable broadcast phase in ACS.
In our system, we wish to understand the scalability properties.
Thus we consider the complexity as a function of $N$ rather than $n$ or $\lambda$.
Since $|v|$ is at most all the CP blocks from every node, we have $|v| = cN$,
where $c$ is a constant representing the size of one CP block.
Therefore the communication complexity of ACS in our system is $O(N)$.
Since we use a constant $n$, $O(N)$ communication complexity also holds for a single facilitator.

@@

\subsection{Time Complexity of ACS}
\label{sec:acs-time-complexity}
In order to make arguments on bandwidth or throughput, which are concepts that depend on time,
we must make some assumptions on the time complexity of ACS.
The time complexity we use here is not the same as what is typically used in distributed systems.
In analysis of distributed systems, time complexity is often in number of rounds.
For example, ACS runs in a constant number of rounds because its subprotocols---reliable broadcast and binary Byzantine consensus---also run in a constant number of rounds.
However, in practice, making a unit of communication always has some overhead associated with it, for example serialising and writing it to some network socket.
Hence, for the remainder of our performance analysis, add the following to our computational model.
For every unit of communication, we assume they take some non-negligible but constant time to perform.
From our result in \Cref{sec:acs-complexity} and the fact that ACS runs in a constant number of rounds,
it follows that ACS has a time complexity of $O(N)$.

\subsection{Bandwidth Requirement for Transactions}
With our assumption on the time complexity of ACS,
we are ready to analyse the bandwidth.
We know that to create and then validate a transaction, the bandwidth required is of $O(l)$,
where $l$ is the length of the agreed fragment.
This can be seen from the fact that the largest message by far is the \texttt{vd\_resp} message,
which contains the agreed fragment,
the other messages (\texttt{tx\_req}, \texttt{tx\_resp} and \texttt{vd\_req}) are constant factors.
If we assume that every node performs transactions at a constant rate of $r_{\text{tx}}$ per second.
Then
$$l = r_{\text{tx}} D_{\text{acs}},$$
where $D_{\text{acs}}$ is the duration an instance of ACS.
But from \Cref{sec:acs-time-complexity},
we know that $D_{\text{acs}}$ is of $O(N)$, thus the bandwidth per transaction is $O(N)$.
% TODO how does message complexity translate to time complexity?
% TODO computational task minimal compared to messages, thus the sending of message is expensive?
This is intuitive because consensus duration would be longer if there are more CP blocks, which means that the agreed fragments are longer (assuming nodes transact at a constant rate).
This behaviour is also verified experimentally in \Cref{ch:implementation}.

\subsection{Global Throughput}
Using our results so far, we are able to analyse the global throughput.
Suppose every node has some fixed bandwidth capacity $C$ (unit of communication per second),
they make transactions at $r_{\text{tx}}$ per second.
Then we have the inequality $C \ge r_{\text{tx}} l$, where $l$ is the length of the the agree fragment as before.
Rearranging, we get
$$\frac{C}{l} \ge r_{\text{tx}}.$$
With this, we consider two cases, first is  when all the nodes are running at maximum capacity, i.e. $\frac{C}{l} = r_{\text{tx}}$.
Recall that $l$ is of $O(N)$, so as the the population increases, 
the transaction rate must decrease in order to maintain the inverse relationship,
thus $r_\text{tx}$ is of $O(N^{-1})$. % TODO is this formal? use omega?
Therefore, the global throughput would be $O(N^{-1})N = O(1)$.
In the second case, nodes are not running at maximum capacity and $r_{\text{tx}}$ is maintained.
Therefore, if every node runs at $r_{\text{tx}}$,
the global throughput becomes $O(N)$ until $N$ is too large and we go back to the first case.
A visualisation of the result is shown in \Cref{fig:throughput-visualisation}.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.7\textwidth]{throughput-visualisation}
  \caption{Visualisation of the worst case global throughput.}
  \label{fig:throughput-visualisation}
\end{figure}
